GSE158420: RNA expression downsampling

### 2024-07-17 analysis/GSE158420_rna.Rmd
add data
fix

@@

ores <- do.call(rbind,ores)
rownames(ores) <- sizes
colnames(ores) <- c("up","dn")
ores <- as.data.frame(ores)
ores$tot <- ores$up + ores$dn
tot <- fres$tot
names(tot) <- sizes
par(mar=c(mar = c(5.1, 5.1, 4.1, 2.1)))
barplot(tot,horiz=TRUE,las=1,xlab="no. pathways FDR<0.05",ylab="no. genes selected")

@@

ssres <- fgres
dots <- lapply(ssres,function(x) { x[,"TP"] })
fgres2 <- do.call(rbind,lapply(dots,summary))

@@

>>>>

fres <- fgsea(pathways=gs,stats=stat,minSize=5, nproc=8)

@@

ores <- do.call(rbind,ores)
rownames(ores) <- sizes
colnames(ores) <- c("up","dn")
ores <- as.data.frame(ores)
ores$tot <- ores$up + ores$dn
tot <- ores$tot
names(tot) <- sizes
par(mar=c(mar = c(5.1, 5.1, 4.1, 2.1)))
barplot(tot,horiz=TRUE,las=1,xlab="no. pathways FDR<0.05",ylab="no. genes selected")

@@

ssres <- fgres

@@

df
